Selecting Computations: Theory and Applications

### 2012-06-27 paper/vago.uai/abstract.tex
9 pages

\begin{abstract}
Sequential decision problems are often approximately solvable by
simulating possible future action sequences.  {\em Metalevel} decision
procedures have been developed for selecting {\em which} action
sequences to simulate, based on estimating the expected
improvement in decision quality that would result from any particular
simulation; an example is the recent work on using bandit algorithms
to control Monte Carlo tree search in the
game of Go.  In this paper we develop a theoretical basis for
metalevel decisions in the statistical framework of {\em selection problems}, 
arguing (as others have done) that this is more appropriate than the bandit
framework.  We derive a number of basic results applicable to 
Monte Carlo selection problems, including the first finite sampling
bounds for optimal policies in certain cases; we also provide a simple
counterexample to the intuitive conjecture that an optimal policy will
necessarily reach a decision in all cases.  We then derive heuristic
approximations in both Bayesian and distribution-free settings and
demonstrate their superiority to bandit-based heuristics in one-shot
decision problems and in Go.
\end{abstract}

>>>>

\begin{abstract}
Sequential decision problems are often approximately solvable by
simulating possible future action sequences.  {\em Metalevel} decision
procedures have been developed for selecting {\em which} action
sequences to simulate, based on estimating the expected
improvement in decision quality that would result from any particular
simulation; an example is the recent work on using bandit algorithms
to control Monte Carlo tree search in the
game of Go.  In this paper we develop a theoretical basis for
metalevel decisions in the statistical framework of Bayesian {\em selection problems}, 
arguing (as others have done) that this is more appropriate than the bandit
framework.  We derive a number of basic results applicable to 
Monte Carlo selection problems, including the first finite sampling
bounds for optimal policies in certain cases; we also provide a simple
counterexample to the intuitive conjecture that an optimal policy will
necessarily reach a decision in all cases.  We then derive heuristic
approximations in both Bayesian and distribution-free settings and
demonstrate their superiority to bandit-based heuristics in one-shot
decision problems and in Go.
\end{abstract}

### 2012-06-27 paper/vago.uai/introduction.tex
9 pages

Analyzing the metalevel problem within an appropriate theoretical
framework ought to lead to more effective algorithms than those
obtained within the bandit framework.  For Monte Carlo computations,
in which samples are gathered to estimate the utilities of actions,
the metalevel decision problem is an instance of the {\em selection
problem} studied in statistics~\citep{Bechhofer:1954,Swisher+et+al:2003}.  Despite
some recent work \citep{Frazier+Powell:2010,TolpinShimony:2012}, the theory of selection
problems is less well understood than that of bandit problems.
Most work has focused on the probability of selection error rather than
optimal policies~\citep{Bubeck+al:2011}.
Accordingly, we present in \secrefs{sec:optimal}{sec:context}
a number of results concerning optimal policies for the general case
as well as specific finite
bounds on the number of samples collected by optimal policies for
Bernoulli arms with beta priors. We also provide a simple
counterexample to the intuitive conjecture that an optimal policy
should not spend more on deciding than the decision is worth; in fact,
it is possible for an optimal policy to compute forever. We also show
by counterexample that optimal {\em index
policies}~\citep{Gittins:1989} may not exist for selection
problems.

@@

(Proofs omitted due to space constraints can be found in the supplementary material.)

>>>>

Analyzing the metalevel problem within an appropriate theoretical
framework ought to lead to more effective algorithms than those
obtained within the bandit framework.  For Monte Carlo computations,
in which samples are gathered to estimate the utilities of actions,
the metalevel decision problem is an instance of the {\em selection
problem} studied in statistics~\citep{Bechhofer:1954,Swisher+et+al:2003}.  Despite
some recent work \citep{Frazier+Powell:2010,TolpinShimony:2012}, the theory of selection
problems is less well understood than that of bandit problems.
Most work has focused on the probability of selection error rather than
optimal policies in the Bayesian setting~\citep{Bubeck+al:2011}.
Accordingly, we present in \secrefs{sec:optimal}{sec:context}
a number of results concerning optimal policies for the general case
as well as specific finite
bounds on the number of samples collected by optimal policies for
Bernoulli arms with beta priors.  We also provide a simple
counterexample to the intuitive conjecture that an optimal policy
should not spend more on deciding than the decision is worth; in fact,
it is possible for an optimal policy to compute forever. We also show
by counterexample that optimal {\em index
policies}~\citep{Gittins:1989} may not exist for selection
problems.

@@

%% (Proofs omitted due to space constraints can be found in the supplementary material.)

### 2012-06-27 paper/vago.uai/optimalpolicies.tex
9 pages

\begin{dfn} \label{dfn:metalevel-model}
	A \term{metalevel probability model} is a tuple $(U_1,\dots,U_k,\Evidence)$ 
	consisting of jointly distributed random variables:
	\begin{itemize}
		\item Real random variables $U_1,\dots,U_k$, where $U_i$ is the utility of arm~$i$, and
		\item A countable set $\Evidence$ of random variables, each variable $E\in\Evidence$ being 
		      a computation that can be performed and whose value is the result of that computation.
	\end{itemize}
\end{dfn}
%% Not actually true that we necessarily define this with U's as roots:  in sampling models they are naturally /leaves/.
%% Bounedness assumption
For simplicity, in the below we'll assume the utilities $U_i$ are bounded, 
without loss of generality in $[0,1]$.

\begin{example}[Bernoulli sampling]\label{example:bernoulli}
%% One simple metalevel probability model is used as a model of the results of simulations \citep{someone}.
In the \term{Bernoulli metalevel probability model},
each arm will either succeed or not $U_i\in\{0,1\}$, with an unknown latent frequency of success $\Theta_i$, 
and stochastic simulations of possible consequences $E_{ij}$ can be performed:
\begin{align*}
	\Theta_i &\iid {\rm Uniform}[0,1]                      &&\quad\text{for $i\in\{1,\dots,k\}$}\\
	U_i \given \Theta_i &\sample {\rm Bernoulli}(\Theta_i) &&\quad\text{for $i\in\{1,\dots,k\}$}\\
	E_{ij} \given \Theta_i &\iid {\rm Bernoulli}(\Theta_i) &&\quad\text{for $i\in\{1,\dots,k\}$, $j\in\Nat$}
\end{align*}

@@

A metalevel probability model, when combined with a cost of computation $c>0$,%
\footnote{The assumption of a fixed cost of computation is a simplification; 
	precise conditions for its validity are given by \citet{Harada:1997}.} 
defines a metalevel decision problem: what is the optimal strategy with which to choose a sequence 
of computations $E\in\Evidence$ in order to maximize the agent's net utility?
Intuitively, this strategy should choose the computations that give the most evidence relevant
to deciding which arm to use, stopping when the cost of computation 
outweighs the benefit gained. We formalize the selection problem as a Markov Decision Process (MDP; 
see, e.g., \citet{Puterman:1994}):

@@

@@

\begin{proof}
	Follows immediately from \eqref{eq:value-fn} and the definition of the
	reward function in \dfnref{dfn:metalevel-mdp}.
\end{proof}

@@

@@

\begin{proof}
	The first follows as in state $s$ the optimal policy has value at least that
	of stopping immediately ($\max_i \mu_i(s)$), and as $\IE \max_i\mu_i(S_N) \le \IE \max_i U_i$ by Jensen's inequality.
	The second from \thmref{thm:value-of-computation}.
\end{proof}

@@

The myopic policy takes the best action, to either stop or perform a computation,
under the assumption that at most one further computation can be performed.
It has a tendency to stop too early, because changing one's mind about which real action to take often takes more than one computation.
In fact, we have:

@@

Using this, we can prove our bound:

\begin{thm}\label{thm:one-action-bound}
	The one-armed Bernoulli decision process with constant arm $\lambda\in[0,1]$ 
	performs at most $\lambda(1-\lambda)/c-3 \le 1/4c-3$ computations.
\end{thm}
\begin{proof}
Using \dfnref{dfn:myopic} and \exampleref{example:bernoulli2}, we determine
which states the myopic policy stops in by bounding $Q^m(s,E)$.  For a state $(s,f)$,
let $\mu=(s+1)/(n+2)$ be the mean utility for arm~2, where $n=s+f$.
Fixing $n$ and maximizing over $\mu$, we get sufficient condition for stopping
\begin{equation}
	c \ge \frac{\lambda(1-\lambda)}{(n+3)} \qquad\qquad   n\ge \frac{\lambda(1-\lambda)}{c} - 3  \label{eq:myopic-stopping}
\end{equation}
Since the set of states satisfying \eqref{eq:myopic-stopping} is closed under
transitions ($n$ only increases), by \thmref{thm:optimal-myopic}.  Finally, note $\max_{\lambda\in[0,1]} \lambda(1-\lambda)=1/4$.
\end{proof}

@@

A key implication is that the \emph{optimal} policy can be computed
in time $O(1/c^2)$, i.e., quadratic in the inverse cost.  This is particularly appropriate when the cost of 
computation is relatively high, such as in simulation experiments \citep{Swisher+et+al:2003},
or when the decision to be made is critical. Finite bounds for the $k$-armed problem
can also be derived and will be included in the full paper.

>>>>

\begin{dfn} \label{dfn:metalevel-model}
	A \term{metalevel probability model} is a tuple $(U_1,\dots,U_k,\Evidence)$ 
	consisting of jointly distributed random variables:
	\begin{itemize}
		\item Real random variables $U_1,\dots,U_k$, where $U_i$ is the utility of arm~$i$, and
		\item A countable set $\Evidence$ of random variables, each variable $E\in\Evidence$ being 
		      a computation that can be performed and whose value is the result of that computation.
	\end{itemize}
\end{dfn}
%% Not actually true that we necessarily define this with U's as roots:  in sampling models they are naturally /leaves/.
%% Bounedness assumption
For simplicity, in the below we'll assume the utilities $U_i$ are bounded, 
without loss of generality in $[0,1]$.  We will abuse notation and denote by $e\in E$ that $e$ is
a potential value of the computation $E$.

\begin{example}[Bernoulli sampling]\label{example:bernoulli}
%% One simple metalevel probability model is used as a model of the results of simulations \citep{someone}.
In the \term{Bernoulli metalevel probability model},
each arm will either succeed or not $U_i\in\{0,1\}$, with an unknown latent frequency of success $\Theta_i$, 
and a set of stochastic simulations of possible consequences
$\mathcal{E} = \{E_{ij} | 1\le i \le k, j\in \mathbb{N}\}$ that can be performed:
\begin{align*}
	\Theta_i &\iid {\rm Uniform}[0,1]                      &&\quad\text{for $i\in\{1,\dots,k\}$}\\
	U_i \given \Theta_i &\sample {\rm Bernoulli}(\Theta_i) &&\quad\text{for $i\in\{1,\dots,k\}$}\\
	E_{ij} \given \Theta_i &\iid {\rm Bernoulli}(\Theta_i) &&\quad\text{for $i\in\{1,\dots,k\}$, $j\in\Nat$}
\end{align*}

@@

A metalevel probability model, when combined with a cost of computation $c>0$,%
\footnote{The assumption of a fixed cost of computation is a simplification; 
	precise conditions for its validity are given by \citet{Harada:1997}.} 
defines a metalevel decision problem: what is the optimal strategy with which to choose a sequence 
of computations $E\in\Evidence$ in order to maximize the agent's net utility?
Intuitively, this strategy should choose the computations that give the most evidence relevant
to deciding which arm to use, stopping when the cost of computation 
outweighs the benefit gained. We formalize the selection problem as a Markov Decision Process
(see, e.g., \citet{Puterman:1994}):

@@

Note that when stopping in state $s$, the expected utility of 
action $i$ is by definition $\mu_i(s)$, so the optimal action to take is $i^*\in\argmax_i \mu_i(s)$
which has expected utility $\mu_{i*}(s) = \max_i\mu_i(s)$.

@@

\begin{hiddenproof}
	Follows immediately from \eqref{eq:value-fn} and the definition of the
	reward function in \dfnref{dfn:metalevel-mdp}.
\end{hiddenproof}

@@

%%This immediately raises the question of whether
%%one can solve for an optimal policy, and whether it is sometimes optima
%%to perform infinitely many computations.

@@

\begin{hiddenproof}
	The first follows as in state $s$ the optimal policy has value at least that
	of stopping immediately ($\max_i \mu_i(s)$), and as $\IE \max_i\mu_i(S_N) \le \IE \max_i U_i$ by Jensen's inequality.
	The second from \thmref{thm:value-of-computation}.
\end{hiddenproof}

@@

The myopic policy (known the metalevel greedy approximation with single-step
assumption in \cite{Russell+Wefald:1991a}) takes the best action, to either stop or perform a computation,
under the assumption that at most one further computation can be performed.
It has a tendency to stop too early, because changing one's mind about which real action to take often takes more than one computation.
In fact, we have:

@@

Using these results connecting the behavior of the optimal and myopic policies, we can prove our bound:

\begin{thm}\label{thm:one-action-bound}
	The one-armed Bernoulli decision process with constant arm $\lambda\in[0,1]$ 
	performs at most $\lambda(1-\lambda)/c-3 \le 1/4c-3$ computations.
\end{thm}
\begin{proof}
Using \dfnref{dfn:myopic} and \exampleref{example:bernoulli2}, we determine
which states the myopic policy stops in by bounding $Q^m(s,E)$.  For a state $(s,f)$,
let $\mu=(s+1)/(n+2)$ be the mean utility for arm~2, where $n=s+f$.
Fixing $n$ and maximizing over $\mu$, we get sufficient condition for stopping
Since the set of states satisfying \eqref{eq:myopic-stopping} is closed under
\begin{equation}
	c \ge \frac{\lambda(1-\lambda)}{(n+3)} \qquad\qquad   n\ge \frac{\lambda(1-\lambda)}{c} - 3  \label{eq:myopic-stopping}
\end{equation}
Since the set of states satisfying \eqref{eq:myopic-stopping} is closed under
transitions ($n$ only increases), by \thmref{thm:optimal-myopic}.  Finally, note $\max_{\lambda\in[0,1]} \lambda(1-\lambda)=1/4$.
\end{proof}

@@

A key implication is that the \emph{optimal} policy can be computed
in time $O(1/c^2)$, i.e., quadratic in the inverse cost.  This is particularly appropriate when the cost of 
computation is relatively high, such as in simulation experiments \citep{Swisher+et+al:2003},
or when the decision to be made is critical.

%% Finite bounds for the $k$-armed problem
%% can also be derived and will be included in the full paper.

### 2012-06-27 paper/vago.uai/paper.tex
9 pages

\title{Selecting Computations: Theory and Applications} 
\author{ {\bf Nicholas Hay} and {\bf Stuart Russell} \\   
Computer Science Division \\  
University of California\\ 
Berkeley, CA 94720 \\ 
\And 
{\bf David Tolpin} and {\bf Solomon Eyal Shimony} \\ 
Department of Computer Science \\ 
Ben-Gurion University of the Negev\\
Beer Sheva 84105, Israel
}

@@

Our bounds below are applicable to any bounded distribution (without loss of generality 
bounded in $[0,1]$). Similar
bounds can be derived for certain unbounded distributions, such as the
normally distributed prior value with normally distributed
sampling.
We derive a VOI bound for testing an arm a fixed $N$ times,
where $N$ can be the remaining budget of available samples or
any other integer quantity.
Denote by  $\Lambda_i^b$ the intrinsic VOI of testing the $i$th arm
$N$ times, and the number of
samples already taken from the $i$th arm by $n_i$.
\begin{thm} $\Lambda_i^b$ is bounded from above as
\begin{align}
\label{eqn:thm-be}
  \Lambda_\alpha^b&\le \frac {N \overline X_\beta^{n_\beta}} {n_\alpha} \Pr(\overline X_\alpha^{n_\alpha+N}\le\overline X_\beta^{n_\beta})\nonumber\\
\Lambda_{i|i\ne\alpha}^b&\le \frac {N(1-\overline X_\alpha^{n_\alpha})} {n_i}\Pr(\overline   X_i^{{n_i}+N}\ge\overline X_\alpha^{n_\alpha})
\end{align}
\label{thm:be}
\end{thm}
\begin{hiddenproof}
	\vspace{-2em}
	\begin{proof} For the case $i\ne \alpha$, the probability that the
	  $i$th arm is finally chosen instead of $\alpha$ is
	  $\Pr(\overline X_i^{n_i+N} \ge \overline X_\alpha^{n_\alpha})$. $X_i \le 1$,
	  therefore $\overline X_i^{n_i+N}\le \overline
	  X_\alpha^{n_\alpha}+\frac {N(1-\overline X_\alpha^{n_\alpha})} {N+n_i}$. Hence, the intrinsic value of blinkered
	  information is at most: 
	\begin{align}
	\label{eq:simplistic}
	\frac{ N(1-\overline  X_\alpha^{n_\alpha})}
	  {N+n_i}&\Pr(\overline X_i^{{n_i}+N}\hspace{-0.5em}\ge\overline X_\alpha^{n_\alpha})\nonumber \\
	&\le\frac{ N(1-\overline  X_\alpha^{n_\alpha})}
	{n_i}\Pr(\overline X_i^{{n_i}+N}\hspace{-0.5em}\ge\overline X_\alpha^{n_\alpha})
	\end{align}
	  Proof for the case $i=\alpha$ is similar.
	\end{proof}		
\end{hiddenproof}

The probabilities can be bounded from above using the
Hoeffding inequality \citep{Hoeffding.ineq}:
\begin{thm} The probabilities in \eqref{eqn:thm-be} are bounded from above as
\begin{align}
  \label{eqn:probound-blnk-hoeffding}
  \Pr&(\overline X_\alpha^{{n_\alpha}+N} \le \overline X_\beta^{n_\beta})
  \le 2\exp\left(- \varphi (\overline X_\alpha^{n_\alpha} - \overline X_\beta^{n_\beta})^2 n_\alpha
  \right)\nonumber\\
  \Pr&(\overline X_{i|i\ne\alpha}^{n_\alpha+N} \ge \overline X_\beta^{n_\beta})
  \le 2\exp\left(- \varphi (\overline X_\alpha^{n_\alpha} -\overline  X_i^{n_i})^2 n_i \right)
\end{align}
where $\varphi=\min \left(2(\frac {1+n/N} {1+\sqrt {n/N}})^2\right)=8(\sqrt 2 - 1)^2 > 1.37$.
\label{thm:hoeffding-prob-bounds}
\end{thm}

@@

\begin{crl}
An upper bound on the VOI estimate $\Lambda_i^b$ is obtained
by substituting \eqref{eqn:probound-blnk-hoeffding} into \eqref{eqn:thm-be}.
\begin{align}
  \label{eqn:bound-blnk-hoeffding}
  \Lambda&_\alpha^b \le \hat\Lambda_\alpha^b=\frac {2N\overline X_\beta^{n_\beta}} {n_\alpha}\exp\left(- \varphi(\overline X_\alpha^{n_\alpha}\hspace{-0.5em} - \overline X_\beta^{n_\beta})^2 n_\alpha\right)\nonumber\\
  \Lambda&_{i|i\ne\alpha}^b\le \hat\Lambda_i^b=  \frac {2N(1-\overline  X_\alpha^{n_\alpha})} {n_i}\exp\left(- \varphi(\overline X_\alpha^{n_\alpha}\hspace{-0.5em} - \overline X_i^{n_i})^2 n_i\right)
\end{align}
\label{crl:bound-blnk-hoeffding}
\end{crl}
\vspace{-2em}

@@

\begin{figure}[h!]
\centering
\includegraphics[scale=0.6]{flat.pdf}
\caption{Average regret of various policies as a function of the fixed number 
of samples in a 25-action Bernoulli sampling problem, over 10000 trials.}
\label{fig:random-instances}
\end{figure}

@@

When a sample has a known cost commensurable with the value of
information of a measurement, an upper bound on the intrinsic VOI can also
be used to stop the sampling if the intrinsic VOI of any arm
is less than the total cost of sampling $C$:
\begin{equation}
\mbox{stop if } \max_i \Lambda_i \le C
\end{equation}
The VOI estimates of \eqrefs{eqn:thm-be}{eqn:bound-blnk-hoeffding} 
include the remaining sample budget $N$ as a
factor, but given the cost of a single sample $c$, the cost of the
remaining samples accounted for in estimating the intrinsic VOI is
$C=cN$. $N$ can be dropped on both sides of the inequality,
giving a reasonable stopping criterion:
\begin{align}
\frac 1 N \Lambda_\alpha^b \le&\frac {\overline X_\beta^{n_\beta}}
  {n_\alpha}\Pr(\overline X_\alpha^{n_\alpha+N}\le\overline
  X_\beta^{n_\alpha})\le c\nonumber\\
\frac 1 N \max_i\Lambda_i^b\le &\max_i\frac {(1-\overline X_\alpha^{n_\alpha})} {n_i}\Pr(\overline
  X_i^{n_i+N}\ge\overline X_\alpha^{n_\alpha})\le c\nonumber\\
    &\forall i: i\ne\alpha
\label{eqn:stopping-blnk}
\end{align}
The empirical evaluation (\secref{sec:empirical-evaluation})
confirms the viability of this stopping criterion and illustrates the
influence of the sample cost $c$ on the performance of
the sampling policy. When the sample cost $c$ is unknown, one can perform initial calibration experiments
to determine a reasonable value, as done in the following.

@@

The hybrid policies were compared on the game Go, a search domain
in which UCT-based MCTS has been particularly successful
\citep{Gelly.mogo}. A modified version of Pachi \citep{Braudis.pachi}, a state of the art
Go program, was used for the experiments:
\begin{itemize}
\item The UCT engine of Pachi was extended with VOI-aware sampling
  policies at the first step. 
\item The stopping criterion for the VOI-aware policy was
  modified and based solely on the sample cost, specified as
  a constant parameter. The heuristic stopping criterion for the
  original UCT policy was left unchanged.
\item The time-allocation model based on the fixed number of samples
  was modified for \textit{both the original UCT policy and the VOI-aware
  policies} such that 
  \begin{itemize}
    \item Initially, the same number of samples is available to
      the agent at each step, independently of the number of pre-simulated
      games;  
    \item If samples were unused at the current step,
      they become available at the next step. 
  \end{itemize}
\end{itemize}
While the UCT engine is not the most powerful engine of Pachi, it is still a strong
player. On the other hand, additional features of more advanced
engines would obstruct the MCTS phenomena which are the subject of
the experiment.
\begin{figure}[h!]
\centering
\includegraphics[scale=0.6]{uctvoi.pdf}
\caption{Winning rate of the VOI-aware policy in Go as a function of the cost $c$, for varying numbers of samples per ply.}
\label{fig:uctvoi}
\end{figure}
The engines were compared on the 9x9 board, for 5000, 7000, 1000, and
15000 samples (game simulations) per ply, each experiment repeated
1000 times. \figref{fig:uctvoi} depicts a calibration experiment,
showing the winning rate of the VOI-aware policy against UCT as a function of
the stopping threshold $c$ (if the maximum VOI of a sample is below
the threshold, the simulation is stopped, and a move is chosen). Each
curve in the figure corresponds to a certain number of samples per
ply.  For the stopping threshold of $10^{-6}$, the VOI-aware policy
is almost always better than UCT, and reaches the winning rate of
64\% for 10000 samples per ply.

\begin{figure}[h!]
\centering
\includegraphics[scale=0.6]{voi-wins.pdf}
\caption{Winning rate of the VOI-aware policy in Go as a function of the number of samples, fixing cost $c=10^{-6}$.}
\label{fig:voi-wins}
\end{figure}

>>>>

\title{Selecting Computations: Theory and Applications} 
\author{ {\bf Nicholas Hay} and {\bf Stuart Russell} \\   
Computer Science Division \\  
University of California\\ 
Berkeley, CA 94720\\
\texttt{\{nickjhay,russell\}@cs.berkeley.edu}
\And 
{\bf David Tolpin} and {\bf Solomon Eyal Shimony} \\ 
Department of Computer Science \\ 
Ben-Gurion University of the Negev\\
Beer Sheva 84105, Israel\\
\texttt{\{tolpin,shimony\}@cs.bgu.ac.il}
}

@@

Our bounds below are applicable to any bounded distribution (without loss of generality 
bounded in $[0,1]$). Similar
bounds can be derived for certain unbounded distributions, such as the
normally distributed prior value with normally distributed
sampling.
We derive a VOI bound for testing an arm a fixed $N$ times,
where $N$ can be the remaining budget of available samples or
any other integer quantity.
Denote by  $\Lambda_i^b$ the intrinsic VOI of testing the $i$th arm
$N$ times, and the number of
samples already taken from the $i$th arm by $n_i$.
\begin{thm} $\Lambda_i^b$ is bounded from above as
\begin{align}
\label{eqn:thm-be}
  \Lambda_\alpha^b&\le \frac {N \overline X_\beta^{n_\beta}} {n_\alpha} \Pr(\overline X_\alpha^{n_\alpha+N}\le\overline X_\beta^{n_\beta})\nonumber\\
\Lambda_{i|i\ne\alpha}^b&\le \frac {N(1-\overline X_\alpha^{n_\alpha})} {n_i}\Pr(\overline   X_i^{{n_i}+N}\ge\overline X_\alpha^{n_\alpha})
\end{align}
\vspace{-24pt}
\label{thm:be}
\end{thm}
\begin{hiddenproof}
	\vspace{-2em}
	\begin{proof} For the case $i\ne \alpha$, the probability that the
	  $i$th arm is finally chosen instead of $\alpha$ is
	  $\Pr(\overline X_i^{n_i+N} \ge \overline X_\alpha^{n_\alpha})$. $X_i \le 1$,
	  therefore $\overline X_i^{n_i+N}\le \overline
	  X_\alpha^{n_\alpha}+\frac {N(1-\overline X_\alpha^{n_\alpha})} {N+n_i}$. Hence, the intrinsic value of blinkered
	  information is at most: 
	\begin{align}
	\label{eq:simplistic}
	\frac{ N(1-\overline  X_\alpha^{n_\alpha})}
	  {N+n_i}&\Pr(\overline X_i^{{n_i}+N}\hspace{-0.5em}\ge\overline X_\alpha^{n_\alpha})\nonumber \\
	&\le\frac{ N(1-\overline  X_\alpha^{n_\alpha})}
	{n_i}\Pr(\overline X_i^{{n_i}+N}\hspace{-0.5em}\ge\overline X_\alpha^{n_\alpha})
	\end{align}
	  Proof for the case $i=\alpha$ is similar.
	\end{proof}		
\end{hiddenproof}

The probabilities can be bounded from above using the
Hoeffding inequality \citep{Hoeffding.ineq}:
\begin{thm} The probabilities in \eqref{eqn:thm-be} are bounded from above as
\begin{align}
  \label{eqn:probound-blnk-hoeffding}
  \Pr&(\overline X_\alpha^{{n_\alpha}+N}\hspace{-6pt} \le \overline X_\beta^{n_\beta})
  \le 2\exp\left(- \varphi (\overline X_\alpha^{n_\alpha} - \overline X_\beta^{n_\beta})^2 n_\alpha
  \right)\nonumber\\
  \Pr&(\overline X_{i|i\ne\alpha}^{n_\alpha+N}\hspace{-6pt} \ge \overline X_\beta^{n_\beta})
  \le 2\exp\left(- \varphi (\overline X_\alpha^{n_\alpha} -\overline  X_i^{n_i})^2 n_i \right)\hspace{-6pt}
\end{align}
where $\varphi=\min \left(2(\frac {1+n/N} {1+\sqrt {n/N}})^2\right)=8(\sqrt 2 - 1)^2 > 1.37$.
\label{thm:hoeffding-prob-bounds}
\end{thm}

@@

\begin{crl}
An upper bound on the VOI estimate $\Lambda_i^b$ is obtained
by substituting \eqref{eqn:probound-blnk-hoeffding} into (\ref{eqn:thm-be}).
\begin{align}
  \label{eqn:bound-blnk-hoeffding}
  \Lambda&_\alpha^b \le \hat\Lambda_\alpha^b=\frac {2N\overline X_\beta^{n_\beta}} {n_\alpha}\exp\left(- \varphi(\overline X_\alpha^{n_\alpha}\hspace{-0.5em} - \overline X_\beta^{n_\beta})^2 n_\alpha\right)\\
  \Lambda&_{i|i\ne\alpha}^b\le \hat\Lambda_i^b=  \frac {2N(1-\overline  X_\alpha^{n_\alpha})} {n_i}\exp\left(- \varphi(\overline X_\alpha^{n_\alpha}\hspace{-0.5em} - \overline X_i^{n_i})^2 n_i\right)\nonumber
\end{align}
\label{crl:bound-blnk-hoeffding}
\end{crl}
\vspace{-2em}

@@

\begin{figure}[h!]
\centering
\includegraphics[scale=0.55]{flat.pdf}
\caption{Average regret of various policies as a function of the fixed number 
of samples in a 25-action Bernoulli sampling problem, over 10000 trials.}
\label{fig:random-instances}
\end{figure}

@@

When a sample has a known cost commensurable with the value of
information of a measurement, an upper bound on the intrinsic VOI can also
be used to stop the sampling if the intrinsic VOI of any arm
is less than the total cost of sampling $C$: $\max_i \Lambda_i \le C$.

The VOI estimates of \eqrefs{eqn:thm-be}{eqn:bound-blnk-hoeffding} 
include the remaining sample budget $N$ as a
factor, but given the cost of a single sample $c$, the cost of the
remaining samples accounted for in estimating the intrinsic VOI is
$C=cN$. $N$ can be dropped on both sides of the inequality,
giving a reasonable stopping criterion:
\begin{align}
\frac 1 N \Lambda_\alpha^b \le&\frac {\overline X_\beta^{n_\beta}}
  {n_\alpha}\Pr(\overline X_\alpha^{n_\alpha+N}\le\overline
  X_\beta^{n_\alpha})\le c\nonumber\\
\frac 1 N \max_i\Lambda_i^b\le &\max_i\frac {(1-\overline X_\alpha^{n_\alpha})} {n_i}\Pr(\overline
  X_i^{n_i+N}\ge\overline X_\alpha^{n_\alpha})\le c\nonumber\\
    &\forall i: i\ne\alpha
\label{eqn:stopping-blnk}
\end{align}
The empirical evaluation (\secref{sec:empirical-evaluation})
confirms the viability of this stopping criterion and illustrates the
influence of the sample cost $c$ on the performance of
the sampling policy. When the sample cost $c$ is unknown, one can perform initial calibration experiments
to determine a reasonable value, as done in the following.

@@

The hybrid policies were compared on the game Go, a search domain
in which UCT-based MCTS has been particularly successful
\citep{Gelly.mogo}. A modified version of Pachi \citep{Braudis.pachi}, a state of the art
Go program, was used for the experiments:
\begin{itemize}
\item The UCT engine of Pachi was extended with VOI-aware sampling
  policies at the first step. 
\item The stopping criterion for the VOI-aware policy was
  modified and based solely on the sample cost, specified as
  a constant parameter. The heuristic stopping criterion for the
  original UCT policy was left unchanged.
\item The time-allocation model based on the fixed number of samples
  was modified for \textit{both the original UCT policy and the VOI-aware
  policies} such that 
  \begin{itemize}
    \item Initially, the same number of samples is available to
      the agent at each step, independently of the number of pre-simulated
      games;  
    \item If samples were unused at the current step,
      they become available at the next step. 
  \end{itemize}
\end{itemize}
While the UCT engine is not the most powerful engine of Pachi, it is still a strong
player. On the other hand, additional features of more advanced
engines would obstruct the MCTS phenomena which are the subject of
the experiment.
\begin{figure}[h!]
\centering
\includegraphics[scale=0.55]{uctvoi.pdf}
\caption{Winning rate of the VOI-aware policy in Go as a function of the cost $c$, for varying numbers of samples per ply.}
\label{fig:uctvoi}
\end{figure}
The engines were compared on the 9x9 board, for 5000, 7000, 1000, and
15000 samples (game simulations) per ply, each experiment repeated
1000 times. \figref{fig:uctvoi} depicts a calibration experiment,
showing the winning rate of the VOI-aware policy against UCT as a function of
the stopping threshold $c$ (if the maximum VOI of a sample is below
the threshold, the simulation is stopped, and a move is chosen). Each
curve in the figure corresponds to a certain number of samples per
ply.  For the stopping threshold of $10^{-6}$, the VOI-aware policy
is almost always better than UCT, and reaches the winning rate of
64\% for 10000 samples per ply.

\begin{figure}[h!]
\centering
\includegraphics[scale=0.55]{voi-wins.pdf}
\caption{Winning rate of the VOI-aware policy in Go as a function of the number of samples, fixing cost $c=10^{-6}$.}
\label{fig:voi-wins}
\end{figure}
